---
title: "AKOATS and SASAP Stream Temperature Data"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(leaflet)
library(sf)
library(tidyr)
library(dplyr)
```

# Monitoring Sites

Click on a monitoring site to view information and download the data.

```{r, message = FALSE, warning = FALSE}
temp <- tempfile()
download.file("https://knb.ecoinformatics.org/knb/d1/mn/v2/object/urn%3Auuid%3Af6ab206b-312c-4caf-89c8-89eb9d031aac", temp, quiet = TRUE)
t <- unzip(temp, exdir = tempfile())
shapefile <-
  read_sf(t[grep(".shp", t)]) %>%
  st_transform(crs = 4326)
unlink(temp)

sites <-
  read.csv("../data_access/data_pids.csv") %>% # update data_pids.csv after new data packages published
  drop_na() %>%
  st_as_sf(coords = c("Longitude", "Latitude"),
           crs = "+init=epsg:4326",
           remove = FALSE) %>%
  st_transform(crs = 4326)

sites$link <- paste0('<a href="', sites$URL, '">', paste("Download", sites$FileName), '</a>')

sites$popup <- paste(sep = "<br/>", sites$link, sites$Waterbody,
                     paste0(sites$Start_Year, "-", sites$End_Year), 
                     sites$Contact_person, sites$Contact_email)

# Palette may depend on number of unique contacts
# count(sites, Contact_person)
factpal <- colorFactor("plasma", sites$Contact_person)

m <-
  leaflet(width = "100%") %>%
  addProviderTiles(providers$Esri.WorldTopoMap) %>%
  addPolygons(data = shapefile,
              fillColor = "white",
              fillOpacity = 0.01,
              color = "gray",
              weight = 1,
              opacity = 0.2) %>%
  addCircleMarkers(data = sites,
                   lat = ~Latitude,
                   lng = ~Longitude,
                   fillColor = ~factpal(Contact_person),
                   fillOpacity = 1,
                   stroke = FALSE,
                   radius = 3,
                   popup = ~popup) %>%
  setView(lng = -155, lat = 64, zoom = 4)

m
```

# Data Packages

Metadata for the above data is available in the data packages published on the KNB:

* [Southeast Alaska Long-term Monitoring Network. 2018. In-situ stream temperature monitoring, Southeast Alaska, 2011-2016. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/doi:10.5063/F1FN14DF)
    + Contact: Scott Harris, Southeast Alaska Long-term Monitoring Network

* [Alaska Center for Conservation Science, University of Alaska Anchorage. 2018. In-situ stream temperature monitoring, Southwest Alaska, 2013-2017. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/doi:10.5063/F1028PR9)
    + Contact: Dan Bogan, Alaska Center for Conservation Science

* [Christopher Sergeant. 2018. National Park Service, Southeast Alaska Network, In-situ stream temperature monitoring of the Indian River, Salmon River, and Taiya River, 2010-2016. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/doi:10.5063/F10P0X83)
    + Contact: Christopher Sergeant, National Park Service

* [US Fish and Wildlife Service Office of Subsistence Management. 2018. In-situ stream temperature monitoring at fish weirs, Alaska, 2008-2015. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/doi:10.5063/F1W0944C)
    + Contact: Margaret Perdue, United States Fish and Wildlife Service

* [Alaska Department of Fish and Game. 2018. In-situ stream temperature monitoring, Kodiak Island, Alaska. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/urn:uuid:6a67fcbc-6a2e-4282-b739-486ec9bb02d0)
    + Contact: Heather Finkle, Alaska Department of Fish and Game
    + Contact: Trenten Dodson, Kodiak Regional Aquaculture Association

* [Christopher Arp. 2018. In-situ stream temperature monitoring, North Slope, Alaska, 2011-2017. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/urn:uuid:e8e9f3f5-9b97-4359-be8f-d712d8c4f6fd)
    + Contact: Christopher Arp, University of Alaska Fairbanks

* [National Park Service (NPS), Southwest Alaska Network (SWAN). 2018. In-situ stream temperature monitoring, southwest Alaska. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/urn:uuid:f69e1996-e46f-4c67-9963-5c0c3bc8671a)
    + Contact: Paul Gabriel, National Park Service

* [Cook Inlet Keeper. 2018. In-situ stream temperature monitoring, Cook Inlet, Alaska, 2002-2017. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/urn:uuid:a98c0f5d-a5e6-49ae-8aa2-132875d35476)
    + Contact: Sue Mauger, Cook Inlet Keeper

* [United States Fish and Wildlife Service. 2017. In-situ stream temperature monitoring, Alaska. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/urn:uuid:cb0d6944-db7f-438e-8a82-ec4c39972c1b)
    + Contact: Margaret Perdue, United States Fish and Wildlife Service

* [National Park Service, Central Alaska Network. 2017. In-situ stream temperature monitoring, central Alaska, 2008-2017. Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/urn:uuid:b63d3d3f-f745-425f-a69f-998154895f40)
    + Contact: Trey Simmons, National Park Service

* [U.S. Geological Society. 2017. Daily summaries of stream temperature at sites in Alaska, U.S. Geological Survey (USGS). Knowledge Network for Biocomplexity.](https://knb.ecoinformatics.org/view/urn:uuid:48903077-e89d-4e92-9577-8b8c32cc6c7a)
    + Contact: U.S. Geological Society


# Reading Stream Temperature Data into R

This [vignette](read_data.html) describes how to read the stream temperature data from these packages into R, including how to filter through to the data of interest. Additionally, a template R script for such purposes can be accessed [here](template.R).
